The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-15 paper.tex
update

 The fiducial run (leftmost column) specified in Section \ref{Methodology}\
 shows that the edge of the outermost bubbles is indeed a forward shock,\
 expanding roughly 12.5 kpc above and below the Galactic plane,\
 and with a radius of about 6.8 kpc along the plane.\

 \Cref{fig__profile} shows the profiles cut at the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.\
 The temperature profile indicates that most of the region between the forward shock and the turbulent region\
 is around 0.3-0.4 keV \citep{Miller2016,Kataoka2018}

>>>>

 The fiducial run (leftmost column) with the initial condition specified in Section \ref{Methodology}\
 shows that the edge of the outermost bubbles is indeed a forward shock,\
 expanding 12.5 kpc above and below the Galactic plane,\
 and with a radius of about 6.8 kpc along the plane.\
 We note that the overall extent of the outermost bubbles is comparable to\
 the two spherical objects of a radius 6-7 kpc proposed by \citet{Predehl2020} for modeling the eROSITA bubbles.

 \Cref{fig__profile} shows the profiles) cut at the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.\
 The temperature profile indicates that most of the region between the forward shock and the turbulent region\
 is around 0.3-0.4 keV \citep{Miller2016,Kataoka2018}
